\chapter{Requirements Traceability}
\section{Customer}
\begin{enumerate}[series=requirements, label=\textbf{R.\arabic*}]
	\item The system shall allow customers to line-up remotely in a store queue.
	\newline\textbf{CustomerApp}, \textbf{TokenManager}, \textbf{TicketManager}, \textbf{QueueManager}
	\item The system shall generate a new ticket when a customer enters a queue.
	\newline\textbf{TicketManager}
	\item The system shall allow customers which do not have a smartphone to get a ticket in place.
	\newline\textbf{CustomerApp}, \textbf{TokenManager}, \textbf{TicketManager}
	\item The system shall allow customers to view the number of people lined up in a queue.
	\newline\textbf{CustomerApp}, \textbf{TokenManager}, \textbf{QueueManager}
	\item The system shall give customers an estimated waiting time.
	\newline\textbf{CustomerApp}, \textbf{TokenManager}, \textbf{QueueManager}
	\item The system shall fetch the GPS position while the user has retrieved a store pass.
	\newline\textbf{MapsManager}
	\item The system shall allow customers to leave a queue.
	\newline\textbf{CustomerApp}, \textbf{TokenManager}, \textbf{TicketManager}, \textbf{QueueManager}
	\item The system shall allow customers to filter stores by name.
	\newline\textbf{CustomerApp}, \textbf{TokenManager}, \textbf{View Info Manager}
	\item The system shall notify customers when it's time to leave for the store.
	\newline\textbf{CustomerApp}, \textbf{TokenManager}, \textbf{MapsManager}
	\item The system shall allow customers to book-a-visit to the store and send them the confirmation link and receipt via email.
	\newline\textbf{CustomerApp}, \textbf{TokenManager}, \textbf{BoookingManager}, \textbf{MailManager}
	\item The system shall allow book-a-visit customers to specify the main categories of item they intend to buy.
	\newline\textbf{CustomerApp}, \textbf{TokenManager}
	\item The system shall allow customers to delete a booked visit.
	\newline\textbf{CustomerApp}, \textbf{TokenManager}, \textbf{BoookingManager}
	\item The system shall notify customers when a ticket or booked visit is deleted.
	\newline\textbf{CustomerApp} \textbf{TokenManager}
	\item The system shall accept bookings based onto the already booked category items.
	\newline\textbf{BoookingManager}
\end{enumerate}

\section{Store manager}
\begin{enumerate}[resume*=requirements]
	\item The system shall allow a registered store manager to login by using their credentials.
	\newline\textbf{WebApp}, \textbf{AuthManager}
	\item The system shall allow store managers to view the current status of people inside the store.
	\newline\textbf{WebApp}, \textbf{AuthManager}, \textbf{DashboardManager}
	\item The system shall allow store managers to view the current status of people in the queue.
	\newline\textbf{WebApp}, \textbf{AuthManager}, \textbf{DashboardManager}
	\item The system shall allow store managers to view the booked visits to the store.
	\newline\textbf{WebApp}, \textbf{AuthManager}, \textbf{DashboardManager}
	\item The system shall allow store managers to set a maximum cap of people inside the store.
	\newline\textbf{WebApp}, \textbf{AuthManager}, \textbf{DashboardManager}
	\item The system shall allow store managers to delete tickets and booked visits.
	\newline\textbf{WebApp}, \textbf{AuthManager}, \textbf{DashboardManager}
\end{enumerate}

\section{Store employee}
\begin{enumerate}[resume*=requirements]
	\item The system shall allow a registered store employee to login by using their credentials.
	\newline\textbf{WebApp}, \textbf{StoreApp}, \textbf{AuthManager}
	\item The system shall allow store employee to view the current status of people inside the store.
	\newline\textbf{WebApp}, \textbf{AuthManager}, \textbf{DashboardManager}
	\item The system shall allow store employee to view the current status of people in the queue.
	\newline\textbf{WebApp}, \textbf{AuthManager}, \textbf{DashboardManager}
	\item The system shall allow store employee to scan QR codes.
	\newline\textbf{StoreApp}, \textbf{AuthManager}
	\item The system shall allow store employee to validate store passes.
	\newline\textbf{StoreApp}, \textbf{AuthManager}, \textbf{ScanManager}
\end{enumerate}

\section{CLup admin}
\begin{enumerate}[resume*=requirements]
	\item The system shall allow CLup admins to register new supermarkets.
	\newline\textbf{WebApp}, \textbf{AuthManager}, \textbf{Dashboard Manager}
	\item The system shall generate new manager and staff credential for each supermarket registered.
	\newline\textbf{WebApp}, \textbf{AuthManager}
\end{enumerate}